Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-05-06 main.Rmd
minor

<!-- Pairs of granularities can be categorized as either a *harmony* or *clash*, where harmonies are pairs of granularities that aid exploratory data analysis, and clashes are pairs that are incompatible with each other for exploratory analysis. -->

@@

smart_harmony <- sm %>%
  rank_harmony(harmony_tbl = harmonies,response =  "general_supply_kwh")%>%
  rename(`facet variable` = facet_variable,
         `x-axis variable` = x_variable,
         `facet levels` = facet_levels,
         `x-axis levels` = x_levels,
         `average maximum variation` = mean_max_variation)

>>>>

<!-- Pairs of granularities can be categorized as either a *harmony* or *clash*, where = are pairs of granularities that aid exploratory data analysis, and clashes are pairs that are incompatible with each other for exploratory analysis. -->

@@

smart_harmony <- sm %>%
  rank_harmony(harmony_tbl = harmonies,response =  "general_supply_kwh") %>%
  rename(`facet variable` = facet_variable,
         `x-axis variable` = x_variable,
         `facet levels` = facet_levels,
         `x-axis levels` = x_levels,
         `average maximum variation` = mean_max_variation)
